The connection between star formation rate and dark matter halo mass in the epoch of reionization

### 2015-05-01 paper/ms.tex
figs. 9 and 10: fontsize changed. Gonzales-Perez error bars are pending.

\begin{figure}
\epsscale{1.00}
\plotone{fig/SFR_DMHM_wo.pdf}
\caption{Star formation rate as function of the dark matter halo mass without dust attenuation. 
Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region. 
Comparison with the GALFORM semi-analitical model \citep{Gonzalez14} and a implementation
of abundance matching model \citep{Behroozi13}. }
\label{fig:SFR_DMHM_wo}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/SFR_DMHM_w.pdf}
\caption{Star formation rate as function of the dark matter halo mass with dust attenuation. 
Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region.
Comparison with the GALFORM semi-analitical model \citep{Gonzalez14} and a implementation
of abundance matching model \citep{Behroozi13}. }
\label{fig:_SFR_DMHM_w}
\end{figure}

>>>>

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD1_SFR_DMHM_wo.pdf}
\caption{Star formation rate as function of the dark matter halo mass without dust attenuation. 
Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region. 
Comparison with %the GALFORM semi-analitical model \citep{Gonzalez14} and a
an implementation
of abundance matching model \citep{Behroozi13}. }
\label{fig:SFR_DMHM_wo}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD1_SFR_DMHM_w.pdf}
\caption{Star formation rate as function of the dark matter halo mass with dust attenuation. 
Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region.
Comparison with %the GALFORM semi-analitical model \citep{Gonzalez14} and a
an implementation
of abundance matching model \citep{Behroozi13}. }
\label{fig:_SFR_DMHM_w}
\end{figure}
